### 2024-01-18 outputs/paper/paper.qmd
update outputs

---
title: "My title"
author: Diana Liu
thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Term-Paper-1."
date: 25 January 2024
abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2023 by months."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(opendatatoronto)
library(dplyr)
library(stringr)
```

# Introduction

You can and should cross-reference sections and sub-sections.

The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

Our data is Marriage Licence Statistics from Open Data Toronto (citeopendatatoronto) which contains data sets maintained by the City of Toronto. The Marriage Licence Statistics dataset consists of monthly number of marriage licenses obtained from 2011 to 2023 in the Greater Toronto Area, it was last updated 2024-01-14. No similar data sets could have been used because this dataset is the only one of marriage licences.
```{r}
#| echo: false
marriage_data <- read_csv("outputs/data/cleaned_data.csv")

head(marriage_data)
```

The Marriage Licence Statistics dataset contains only four variables. _id is a unique identifier code given to each marriage license that is issued, we will not need it for our analysis so it is not selected during the data cleaning. CIVIC_CENTRE gives a two letter abbreviation of the city in which the marriage licenses are issued, ET for Etobicoke NY for North York, SC for Scarborough, and TO for Toronto. We will later examine each region separately. MARRIAGE_LICENSES is the variable denoting how many licenses were obtained each month, with a max of ----, min of ------, and average of -------. TIME_PERIOD is the month in which the marriage licenses were obtained in a yyyy-mm date format.

# Results

Our results are summarized in @tbl-modelresults.

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

\newpage

# References

### 2024-01-18 scripts/02-data_cleaning.R

@@ -19,9 +19,7 @@ cleaned_marriages_data <-
   raw_marriages_data |>
   select(CIVIC_CENTRE, MARRIAGE_LICENSES, TIME_PERIOD) |> # we want to select 
   #only the relevant columns: civic_centre, marriage_licenses, and time_period
-  filter(CIVIC_CENTRE == "TO", TIME_PERIOD >= 2023) # We are only interested in
-# Toronto so we filter on TO to get rid of Etobicoke (ET), North York (NY), 
-# and Scarborough (SC)
+  filter(TIME_PERIOD >= 2023)
 # Then we filter on the year because we are only interested in 2023
 
 cleaned_marriages_data$TIME_PERIOD <- str_c(cleaned_marriages_data$TIME_PERIOD,
@@ -32,8 +30,8 @@ cleaned_marriages_data$TIME_PERIOD <- str_c(cleaned_marriages_data$TIME_PERIOD,
 cleaned_marriages_data <-
   cleaned_marriages_data |>
   mutate(TIME_PERIOD = format(as.Date(TIME_PERIOD), format="%B")) |>
-  rename(Month = TIME_PERIOD, Marriages = MARRIAGE_LICENSES) |>
-  select(Month, Marriages)
+  rename(Month = TIME_PERIOD, Marriages = MARRIAGE_LICENSES, Civic_Centre = CIVIC_CENTRE) |>
+  select(Month, Marriages, Civic_Centre)
 # Then we change the date format to only the month, rename the column so they
 # are easier to understand, and get rid of the CIVIC_CENTRE column
 
@@ -42,3 +40,4 @@ head(cleaned_marriages_data)
 
 #### Save data ####
 write_csv(cleaned_marriages_data, "outputs/data/cleaned_data.csv")
+

### 2024-01-18 scripts/03-test_data.R

@@ -18,3 +18,4 @@ marriage_data$Marriages |> min() >= 0
 marriage_data$Marriages |> max() <= 2000
 marriage_data$Marriages |> class() == 'numeric'
 marriage_data$Month |> class() == 'character'
+

### 2024-01-20 outputs/paper/paper.qmd
updated data cleaning script and outputs

@@
 ---
-title: "My title"
+title: "Getting Hitched: Torontonians Prefer to Get Married During Warm Weather"
 author: Diana Liu
@@
 date: 25 January 2024
-abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2023 by months."
+abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2023 by months.
+By dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March), the number of marriage licenses obtained in Toronto increase significantly during warm months, supporting the hypothesis that Torontonians prefer to get married during warm weather.
+Further analysis should be conducted to determine whether or not this results in longer wait times for marriage licenses and more expensive ceremonies as demand is higher during the peak season."
 format: pdf
@@
 
+library(opendatatoronto)
 library(tidyverse)
-library(opendatatoronto)
 library(dplyr)
 library(stringr)
+library(ggplot2)
 ```
@@
 # Introduction
+According to @citebusinessinsider, summer is the hottest time to get married due to more dress options, the option to have an outdoor wedding, and relatively easier travel among other reasons, but is this actually true for a city like Toronto?
+Toronto is a city known for cold weather in the winter with snow from October to March (@citeurbanclimate).
+This means that we expect the amount of marriage licenses obtained in Toronto should increase during the warm months of April through September and decrease during the cold months of October through March.
 
-You can and should cross-reference sections and sub-sections.
+In order to test this hypothesis, we download marriage license data from opendatatoronto, a database maintained by the City of Toronto and analyze the data by plotting the number of licenses against the month in which they were obtained.
+Our results show that our hypothesis is correct with the number of marriage licenses steadily increasing from Febuary to May, peaking in August, then decreasing between August and November before hitting its lowest in January.
+This cyclic nature can be observed for the prior 2 years as well.
+```{r}
+#| echo: false
+#| message: false
 
-The remainder of this paper is structured as follows. @sec-data....
+marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data.csv")
+print(marriage_data)
+```
 
 # Data {#sec-data}
-
-Our data is Marriage Licence Statistics from Open Data Toronto (citeopendatatoronto) which contains data sets maintained by the City of Toronto.
+Our data is Marriage Licence Statistics from Open Data Toronto (@opendatatoronto) which contains data sets maintained by the City of Toronto.
 The Marriage Licence Statistics dataset consists of monthly number of marriage licenses obtained from 2011 to 2023 in the Greater Toronto Area, it was last updated 2024-01-14.
 No similar data sets could have been used because this dataset is the only one of marriage licences.
+The Marriage Licence Statistics dataset contains only four variables: x_id, civic centres, marriage licenses, and date, but only civic centres, marriage licenses, and date were used in our analysis.
+The data was cleaned and analysed using the statistical software R (@R) with the assistance of tidyverse (@tidy), dyplr (@dyplr), ggplot2(@citeggplot2), and stringr (@stringr).
+
+## Civic Centres
+CIVIC_CENTRE is a column a two letter abbreviation of the city in which the marriage licenses are issued, ET for Etobicoke NY for North York, SC for Scarborough, and TO for Toronto.
+Each civic centre has its own row of corresponding date, number of marriage licenses, and id.
+During the data cleaning process, we filter out ET, NY, and SC so we can focus on Toronto.
+After filtering, we will not need the variable anymore.
 ```{r}
 #| echo: false
-marriage_data <- read_csv("outputs/data/cleaned_data.csv")
+#| message: false
+
+raw_marriage_data <- read_csv("/cloud/project/inputs/data/unedited_data.csv")
+head(raw_marriage_data)
+```
+
+## Marriage Licenses
+MARRIAGE_LICENSES is the variable denoting how many licenses were obtained each month, with a max of 1649 certificates obtained, min of 563, and average of 1058.8 in Toronto in 2023.
+Marriage licenses are obtained in the province of Ontario via an online application process followed by an in-person appointment at the Toronto City Hall.
+The actual wedding ceremony is irrelevant for obtaining a marriage license.
+```{r}
+#| echo: false
+#| message: false
+
+marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data.csv")
 
 head(marriage_data)
+summary(marriage_data$Marriages)
 ```
 
-The Marriage Licence Statistics dataset contains only four variables.
-_id is a unique identifier code given to each marriage license that is issued, we will not need it for our analysis so it is not selected during the data cleaning.
-CIVIC_CENTRE gives a two letter abbreviation of the city in which the marriage licenses are issued, ET for Etobicoke NY for North York, SC for Scarborough, and TO for Toronto.
-We will later examine each region separately.
-MARRIAGE_LICENSES is the variable denoting how many licenses were obtained each month, with a max of ----, min of ------, and average of -------.
+## Date (Month)
 TIME_PERIOD is the month in which the marriage licenses were obtained in a yyyy-mm date format.
+When we clean the data, the date is filtered by year to retain only 2023 information, then it is reformatted so that it is the name of the month (e.g.
+'January')
 
@@
 
-Our results are summarized in @tbl-modelresults.
+```{r}
+#| echo: false
+marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data.csv")
+
+marriage_data |>
+  ggplot(aes(x = Month, y = Marriages, label = Marriages)) +
+  geom_point() +
+  geom_path(color = "red") +
+  geom_text(hjust=0, vjust=0) +
+  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
+  labs(x = "Month", y = "Marriages", color = "Country")
+```
 

### 2024-01-20 scripts/00-simulate_data.R

@@ -21,7 +21,7 @@ simulated_marriage_data <-
         seq(as.Date("2023/1/1"), by = "month", length.out = 12), format="%B"
         ),
     Marriages =
-      round(runif(n = 12, min = 0, max = 2000))
+      round(runif(n = 12, min = 563, max = 1649))
   )
 # simulate deviations from an uniform distribution of the number of marriage
 # licenses obtained in Toronto over 12 months
@@ -30,7 +30,7 @@ simulated_marriage_data
 
 #### Test Simulated Data ####
 simulated_marriage_data$Marriages |> min() >= 0
-simulated_marriage_data$Marriages |> max() <= 2000
+simulated_marriage_data$Marriages |> max() <= 1649
 simulated_marriage_data$Marriages |> class() == 'numeric'
 simulated_marriage_data$Month |> class() == 'character'
 

### 2024-01-20 scripts/02-data_cleaning.R

@@ -19,8 +19,8 @@ cleaned_marriages_data <-
   raw_marriages_data |>
   select(CIVIC_CENTRE, MARRIAGE_LICENSES, TIME_PERIOD) |> # we want to select 
   #only the relevant columns: civic_centre, marriage_licenses, and time_period
-  filter(TIME_PERIOD >= 2023)
-# Then we filter on the year because we are only interested in 2023
+  filter(CIVIC_CENTRE == "TO")
+# Then we filter on the civic centre so that we are only left with Toronto
 
 cleaned_marriages_data$TIME_PERIOD <- str_c(cleaned_marriages_data$TIME_PERIOD,
                                             "-01")
@@ -29,15 +29,24 @@ cleaned_marriages_data$TIME_PERIOD <- str_c(cleaned_marriages_data$TIME_PERIOD,
 
 cleaned_marriages_data <-
   cleaned_marriages_data |>
-  mutate(TIME_PERIOD = format(as.Date(TIME_PERIOD), format="%B")) |>
-  rename(Month = TIME_PERIOD, Marriages = MARRIAGE_LICENSES, Civic_Centre = CIVIC_CENTRE) |>
-  select(Month, Marriages, Civic_Centre)
-# Then we change the date format to only the month, rename the column so they
-# are easier to understand, and get rid of the CIVIC_CENTRE column
-
+  rename(Date = TIME_PERIOD, Marriages = MARRIAGE_LICENSES) |>
+  select(Date, Marriages) |>
+  filter(Date >= as.Date("2022-01-01"))
+# We get rid of the CIVIC_CENTRE column and look at the last two years
 head(cleaned_marriages_data)
+
+cleaned_marriages_data_2022 <-
+  cleaned_marriages_data |>
+  filter(Date >= as.Date("2022-01-01"), Date <= as.Date("2022-12-31"))
+head(cleaned_marriages_data_2022)
+
+cleaned_marriages_data_2023 <-
+  cleaned_marriages_data |>
+  filter(Date >= as.Date("2023-01-01"), Date <= as.Date("2023-12-31"))
+head(cleaned_marriages_data_2023)
 
 
 #### Save data ####
-write_csv(cleaned_marriages_data, "outputs/data/cleaned_data.csv")
-
+write_csv(cleaned_marriages_data, "outputs/data/cleaned_data_all_years.csv")
[…]

### 2024-01-20 scripts/03-test_data.R

@@ -3,7 +3,7 @@
 # Author: Diana Liu
 # Date: 17 January 2024
 # Contact: guanzhi.liu@mail.utoronto.ca
-# Pre-requisites: downloaded and cleaned toronto marriage data
+# Pre-requisites: downloaded and cleaned Toronto marriage data
 
 
 #### Workspace setup ####
@@ -14,8 +14,8 @@ library(tidyverse)
 #### Test data ####
 marriage_data <- read_csv("outputs/data/cleaned_data.csv")
 
-marriage_data$Marriages |> min() >= 0
-marriage_data$Marriages |> max() <= 2000
+marriage_data$Marriages |> min() >= 563
+marriage_data$Marriages |> max() <= 1649
 marriage_data$Marriages |> class() == 'numeric'
 marriage_data$Month |> class() == 'character'
 

### 2024-01-22 outputs/paper/paper.qmd
Changes to paper

--- 2024-01-18 outputs/paper/paper.qmd
@@
 ---
-title: "My title"
+title: "Getting Hitched: Torontonians Prefer to Get Married During Warm Weather"
 author: Diana Liu
-thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Term-Paper-1."
+thanks: "Code and data are available at: https://github.com/Diana-Guanzhi-Liu/Analysis-of-Toronto-Marriages"
 date: 25 January 2024
-abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2023 by months."
+abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months.
+By dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March), the number of marriage licenses obtained in Toronto increase significantly during warm months, supporting the hypothesis that Torontonians prefer to get married during warm weather."
 format: pdf
@@
 #| message: false
-
+library(opendatatoronto)
 library(tidyverse)
-library(opendatatoronto)
 library(dplyr)
 library(stringr)
+library(ggplot2)
+library(tinytex)
+library(gt)
 ```
@@
 # Introduction
+According to @citebusinessinsider, summer is the hottest time to get married due to more dress options, the opportunity to have an outdoor wedding, and relatively easier travel among other reasons, but is this actually true in Toronto?
+Toronto is a city known for cold weather in the winter with snow from October to March (@citeurbanclimate).
+This means that we expect the amount of marriage licenses obtained in Toronto should increase during the warm months of April through September and decrease during the cold months of October through March.
+By knowing whether or not more marriages occur during the summer months, prospective couples in Toronto can plan ahead and avoid peak seasons for applying for a marriage license and any delays that result.
 
-You can and should cross-reference sections and sub-sections.
+In the Data section, we download marriage license data from opendatatoronto(@citeopendata), a database maintained by the City of Toronto.
+This dataset features the number of marriage licenses issued in Toronto by month, beginning January 1 2011.
+We will be looking at data from 2023 and 2022, as well as any changes in the number of marriage licenses between the two years.
 
-The remainder of this paper is structured as follows. @sec-data....
+In order to test this hypothesis, we analyzed the data in the Results section by plotting the number of licenses against the month in which they were obtained and connecting the points with a line so we can see the change in the number of marriage licenses from month to month more clearly.
+Since there are only 12 data points in each graph, we are also able to lable each observation with the exact number of marriage licenses issued.
+Then we calculate *****
+
+Our results show that our hypothesis is correct with the number of marriage licenses steadily increasing from Febuary to May, peaking in August, then decreasing between August and November before hitting its lowest in January.
+This cyclic nature can be observed for both 2022 and 2023
 
 # Data {#sec-data}
-
-Our data is Marriage Licence Statistics from Open Data Toronto (citeopendatatoronto) which contains data sets maintained by the City of Toronto.
+Our data is Marriage Licence Statistics from Open Data Toronto (@citeopendata) which contains data sets maintained by the City of Toronto.
 The Marriage Licence Statistics dataset consists of monthly number of marriage licenses obtained from 2011 to 2023 in the Greater Toronto Area, it was last updated 2024-01-14.
 No similar data sets could have been used because this dataset is the only one of marriage licences.
+Looking at (@fig-raw_toronto_marriages), the Marriage Licence Statistics dataset contains only four variables: x_id, civic centres, marriage licenses, and date, but only civic centres, marriage licenses, and date were used in our analysis.
+The data was cleaned and analysed using the statistical software R (@citeR) with the assistance of tidyverse (@citetidy), dyplr (@citedyplr), ggplot2 (@citeggplot2), tinytex (@citetiny), gt (@citegt), and stringr (@stringr).
+
+We selected the past two years due to some 2021 data being missing and the fact that Covid-19 in 2020 caused a significant decrease in the number of marriage licenses that were obtained all year compared to other years (@citesage).
+
+```{r}
+#| label: fig-raw_toronto_marriages
+#| fig-cap: Sample of Raw Marriage License Data in Toronto
+#| echo: false
+#| message: false
+
+raw_marriage_data <- read_csv("/cloud/project/inputs/data/unedited_data.csv")
+gt(head(raw_marriage_data))
+
+```
+
+## Civic Centres
+CIVIC_CENTRE is the second column in @fig-raw_toronto_marriages and contains a two letter abbreviation of the city in which the marriage licenses are issued, ET for Etobicoke, NY for North York, SC for Scarborough, and TO for Toronto.
+Each civic centre has its own row of corresponding date, number of marriage licenses, and id.
+During the data cleaning process, we filter out ET, NY, and SC so we can focus on Toronto.
+After filtering, we will not need the variable anymore (@fig-cleaned_toronto_marriages).
+
+## Marriage Licenses
+MARRIAGE_LICENSES is the 3rd column in @fig-raw_toronto_marriages and denotes how many licenses were obtained.
+It is important to note that obtaining a marriage license is separate from the wedding ceremony itself, but the two often take place consecutively because a marriage license is required in the province of Ontario to become legally married (@citetorontomarriage).
+
+There are 12 observations per year for each month (@fig-cleaned_toronto_marriages_2022).
+This makes 24 observations for 2022-23 between 472 and 1758, with an average of 1043.3 marriage licenses obtained.
+
+## Date (Month)
+TIME_PERIOD is the month in which the marriage licenses were obtained in a yyyy-mm date format.
+When we clean the data, we must add a -dd to the end of each date value in order for the dates to be in an unambiguous format.
+Then the date is filtered by year to separate 2022 and 2023 from the rest of the dataset.
+
+## Cleaned Data
+After the data we need has been cleaned, it is saved into 3 .csv files, one for 2022 and another for 2023, both of which have 12 observations one for each month.
+The third .csv file conains both years and has 24 observations.
+The only columns that remain in any file are Date and Marriages (@fig-cleaned_toronto_marriages_2022).
+
+```{r}
+#| label: fig-cleaned_toronto_marriages_2022
+#| fig-cap: Sample of Cleaned Marriage License Data in Toronto by Month in 2022
+#| echo: false
+#| message: false
+
+cleaned_marriage_data_2022 <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
+gt(head(cleaned_marriage_data_2022))
+```
+
+# Results
+In order to determine if there is a difference in the amount of marriage licenses issued in Toronto between warm months (April to September) compared to cold months (October to March), we plot the number of marriage licenses for each month separately for 2022, 2023 and both years together.
+Then the ploints are connected with a path line to make the shape of changes over time easier to see.
+It is important to note that the lines in the graphs do not represent the actual rate of change between months because there is only one observation for each month.
+## 2022 Marriage Licenses
+(@fig-2022_marriages)
+```{r}
+#| label: fig-2022_marriages
+#| fig-cap: Number of marriage licenses issued in Toronto in 2022
+#| echo: false
+#| message: false
+#| eval: true
+#| warning: false
+marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
+
+marriage_data |>
+  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
+  geom_point() +
+  geom_path(color = "red") +
+  geom_text(hjust=0, vjust=0) +
+  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
+  labs(x = "Month", y = "Marriages", color = "Country")
+```
 ```{r}
 #| echo: false
-marriage_data <- read_csv("outputs/data/cleaned_data.csv")
-
-head(marriage_data)
+#| message: false
+#| include: false
+marriage_data_2022 <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
+summary(marriage_data_2022$Marriages)
+sum(marriage_data_2022$Marriages)
 ```
 
-The Marriage Licence Statistics dataset contains only four variables.
-_id is a unique identifier code given to each marriage license that is issued, we will not need it for our analysis so it is not selected during the data cleaning.
-CIVIC_CENTRE gives a two letter abbreviation of the city in which the marriage licenses are issued, ET for Etobicoke NY for North York, SC for Scarborough, and TO for Toronto.
-We will later examine each region separately.
-MARRIAGE_LICENSES is the variable denoting how many licenses were obtained each month, with a max of ----, min of ------, and average of -------.
-TIME_PERIOD is the month in which the marriage licenses were obtained in a yyyy-mm date format.
+We used ggplot to plot each marriage license observation for each month, then we connected the points so the trend over time is easier to observe.
+Looking at @fig-2022_marriages, we can see that January has the lowest amount marriage licenses being issued of 472.
+A slight increase of 62 licenses occurs in February, followed by an increase in in March of 684, more than doubling the amount in February.
+Then there is a slight plateau for 3 months before another increase to 1658 licenses in June, this is also the max in 2022 and a $1658/472\approx350\%$increase since January.
+There is another plateau which ends in September when the number of licenses falls to 1108.
+This decrease continues to October where the number if licenses plateau once again around 500.
 
-# Results
+When we examine our graph separated into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, February, March), we can see that there is a 219% increase between the number of marriage licenses in cold and warm months
+$$
+Total\ Marriages\ Warm\ Months\ 2022\\
+1265+1269+1658+1507+1656+1108=8463
+\\
+Average=1410.5
+\\
+Total\ Marriages\ Cold\ Months\ 2022\\
+611+476+556+472+536+1220=3871
+\\
+Average=645.2
+\\
+$$
 
-Our results are summarized in @tbl-modelresults.
+## 2023
+```{r}
+#| label: fig-2023_marriages
+#| fig-cap: Number of marriage licenses issued in Toronto in 2023
+#| echo: false
+#| message: false
+#| eval: true
+#| warning: false
+marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data_2023.csv")
+
+marriage_data |>
+  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
+  geom_point() +
+  geom_path(color = "red") +
+  geom_text(hjust=0, vjust=0) +
+  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
+  labs(x = "Month", y = "Marriages", color = "Country")
+```
+
+```{r}
+#| echo: false
+#| message: false
+#| include: false
+marriage_data_2023 <- read_csv("/cloud/project/outputs/data/cleaned_data_2023.csv")
+summary(marriage_data_2023$Marriages)
+sum(marriage_data_2023$Marriages)
+```
+
+2023 is similar to 2022 in terms of the general pattern of increases and decreases in the number of marriage licenses obtained (@fig-2023_marriages).
+Once again January is the min and a large increase from 517 to 929 takes place between February and March.
+This increase continues until it hits 1507 licenses in May where it levels off.
+August is the max with 1649 licenses.
+The decrease like 2022, starts in September and continues until November.
+
+$$
+Total\ Marriages\ Warm\ Months\ 2022\\
+
+\\
+Average=
+\\
+Total\ Marriages\ Cold\ Months\ 2022\\
+
+\\
+Average=
+\\
+$$
 
 # Discussion
+## Summary Statistics
+### 2022
+Examining marriage licenses data from 2022, we find a max of 1658, min of 472, and average of 1028, for a combined total of 12334 licenses.
 
-## First discussion point {#sec-first-point}
+### 2023
+In 2023, there was a max of 1649, min of 563, mean of 1058.8, and total of 12706 marriage licenses issued. 
+```{r}
+#| echo: false
+#| message: false
+#| include: false
+marriage_data_2023 <- read_csv("/cloud/project/outputs/data/cleaned_data_2023.csv")
+summary(marriage_data_2023$Marriages)
+sum(marriage_data_2023$Marriages)
+```
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+### Both Years
+Compared with the 2022 data, the total number of marriage licenses changed by $(12334-12706)/12706 = −0.0292\approx-2.92\%$.
+This small amount of change indicates that approximately the same number of couples get married in Toronto each year, so any increases in the number of marriages for any given month is unlikely to be attributable to a total increase in marriages.
 
@@
 
-\appendix
-
-# Appendix {-}
-
-# Additional data details
-
-# Model details {#sec-model-details}
-
-## Posterior predictive check
-
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
-
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
-
-\newpage
-
 # References

### 2024-01-22 scripts/00-simulate_data.R

@@ -21,7 +21,7 @@ simulated_marriage_data <-
         seq(as.Date("2023/1/1"), by = "month", length.out = 12), format="%B"
         ),
     Marriages =
-      round(runif(n = 12, min = 563, max = 1649))
+      round(runif(n = 12, min = 0, max = 1758))
   )
 # simulate deviations from an uniform distribution of the number of marriage
 # licenses obtained in Toronto over 12 months
@@ -30,7 +30,7 @@ simulated_marriage_data
 
 #### Test Simulated Data ####
 simulated_marriage_data$Marriages |> min() >= 0
-simulated_marriage_data$Marriages |> max() <= 1649
+simulated_marriage_data$Marriages |> max() <= 1758
 simulated_marriage_data$Marriages |> class() == 'numeric'
 simulated_marriage_data$Month |> class() == 'character'
 

### 2024-01-22 outputs/paper/paper.qmd
additional writing

@@
 
-In order to test this hypothesis, we analyzed the data in the Results section by plotting the number of licenses against the month in which they were obtained and connecting the points with a line so we can see the change in the number of marriage licenses from month to month more clearly.
-Since there are only 12 data points in each graph, we are also able to lable each observation with the exact number of marriage licenses issued.
-Then we calculate *****
+We formulate our hypothesis to be that there are more marriage licenses obtained in warm months of April to September than cold months of October to March because Torontonians prefer to get married during the warmer half of the year.
+We analyzed the data in the Results section by plotting the number of licenses against the month in which they were obtained so we can see the change in the number of marriage licenses from month to month.
+Since there are only 12 data points in each graph, we are also able to label each observation with the exact number of marriage licenses issued.
+Then we calculated the total amount and the average amount of marriage licenses in the warm months and cold months of each year, and the percent change between them.
+Our results show that our hypothesis is correct with the number of marriage licenses steadily increasing from February to May, peaking around July, then decreasing between September and November before hitting its lowest in January.
+This cyclic nature can be observed for both 2022 and 2023.
 
-Our results show that our hypothesis is correct with the number of marriage licenses steadily increasing from Febuary to May, peaking in August, then decreasing between August and November before hitting its lowest in January.
-This cyclic nature can be observed for both 2022 and 2023
+*** Discussion Section
 
@@
 ## Cleaned Data
-After the data we need has been cleaned, it is saved into 3 .csv files, one for 2022 and another for 2023, both of which have 12 observations one for each month.
-The third .csv file conains both years and has 24 observations.
-The only columns that remain in any file are Date and Marriages (@fig-cleaned_toronto_marriages_2022).
 
@@
 ```
+After the data we need has been cleaned, it is saved into 3 .csv files, one for 2022 and another for 2023, both of which have 12 observations one for each month.
+The third .csv file conains both years and has 24 observations.
+The only columns that remain in any file are Date and Marriages (@fig-cleaned_toronto_marriages_2022).
 
@@
 In order to determine if there is a difference in the amount of marriage licenses issued in Toronto between warm months (April to September) compared to cold months (October to March), we plot the number of marriage licenses for each month separately for 2022, 2023 and both years together.
-Then the ploints are connected with a path line to make the shape of changes over time easier to see.
-It is important to note that the lines in the graphs do not represent the actual rate of change between months because there is only one observation for each month.
+
 ## 2022 Marriage Licenses
@@
   geom_point() +
-  geom_path(color = "red") +
   geom_text(hjust=0, vjust=0) +
@@
 
-When we examine our graph separated into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, February, March), we can see that there is a 219% increase between the number of marriage licenses in cold and warm months
+When we examine our graph separated into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, February, March), we can see that there is a $(8463-3871)/3871 \approx 117\%$ increase between the number of marriage licenses in cold and warm months
 $$
-Total\ Marriages\ Warm\ Months\ 2022\\
-1265+1269+1658+1507+1656+1108=8463
+\begin{aligned}
+Total\ Marriages\ Warm\ Months\ &2022\\
+1265+1269+1658+1507+1656+1108&=8463
 \\
-Average=1410.5
+Average&=1410.5
 \\
-Total\ Marriages\ Cold\ Months\ 2022\\
-611+476+556+472+536+1220=3871
+Total\ Marriages\ Cold\ Months\ &2022\\
+611+476+556+472+536+1220&=3871
 \\
-Average=645.2
-\\
+Average&=645.2
+\end{aligned}
 $$
@@
 
+In 2023 there is a $(7026-4146)/4146\approx68\%$ increase between warm and cold months.
+
 $$
-Total\ Marriages\ Warm\ Months\ 2022\\
+\begin{aligned}
+Total\ Marriages\ Warm\ Months\ &2023\\
+1086+1507+1507+1628+1649+1156&=7026
+\\
+Average&=1171
+\\
+Total\ Marriages\ Cold\ Months\ &2023\\
+811+606+647+563+617+929&=4146
+\\
+Average&=691
+\end{aligned}
+$$
+The results indicate that our hypothesis is correct. There are more marriage licenses issued in warm months (April to September) than cold months (October to March).
 
-\\
-Average=
-\\
-Total\ Marriages\ Cold\ Months\ 2022\\
+## Both Years
+```{r}
+#| label: fig-marriages
+#| fig-cap: Number of marriage licenses issued in Toronto in 2022 and 2023
+#| echo: false
+#| message: false
+#| eval: true
+#| warning: false
+marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data_all_years.csv")
 
-\\
-Average=
-\\
-$$
+marriage_data |>
+  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
+  geom_point() +
+  geom_path(color = 'red') +
+  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
+  labs(x = "Month", y = "Marriages", color = "Country")
+```
+Combining both years, we generate another graph to plot the number of marriage licenses and connect the points with a line so the trend over time is easier to see.
+It is important to note that the line only connect the points and do not represent the rate of change.
+This cyclical nature of more marriage licenses obtained in warm months is evident (@fig-marriages)
 
 # Discussion
-## Summary Statistics
-### 2022
-Examining marriage licenses data from 2022, we find a max of 1658, min of 472, and average of 1028, for a combined total of 12334 licenses.
+## Findings
+In both 2022 and 2023, there was more marriage licenses issued in warm months than cold ones, 117% more in 2022 and 68% more in 2023.
+This confirms our hypothesis of more marriages taking place from April to September.
 
-### 2023
-In 2023, there was a max of 1649, min of 563, mean of 1058.8, and total of 12706 marriage licenses issued. 
-```{r}
-#| echo: false
-#| message: false
-#| include: false
-marriage_data_2023 <- read_csv("/cloud/project/outputs/data/cleaned_data_2023.csv")
-summary(marriage_data_2023$Marriages)
-sum(marriage_data_2023$Marriages)
-```
-
-### Both Years
-Compared with the 2022 data, the total number of marriage licenses changed by $(12334-12706)/12706 = −0.0292\approx-2.92\%$.
+Compared with the 2022 data, the total number of marriage licenses in 2023 only changed by $(12334-12706)/12706 = −0.0292\approx-2.92\%$.
 This small amount of change indicates that approximately the same number of couples get married in Toronto each year, so any increases in the number of marriages for any given month is unlikely to be attributable to a total increase in marriages.
 
-## Second discussion point
+With these findings we can conclude that April to September is the busy season for marriage license applications and October to March is the less busy season.
+Since applying for a marriage license comes before the actual wedding ceremony, we can infer that more licenses equate to more weddings.
+This means that there is more demand for venues, photographers, and catering for weddings from April to September making these services harder to book and potentially more expensive.
 
-## Third discussion point
+Prospective couples should consider the trend of higher volume marriage license applications in the warm months when applying for their marriage license because although many Torontonians prefer getting married in the warm month, the higher volume of marriage license application could cause delays.
+The higher demand for wedding ceremonies should also be a part of budgeting for their weddings.
 
-## Weaknesses and next steps
+## Weaknesses and Next Steps
+A weakness in our analysis is the small quantity of data that was used to come to our conclusion.
+While the pattern of increased marriage licenses was present in both 2022 and 2023, this might not have been the case in prior years.
+Performing the same analysis on years 2011 to 2021 will confirm our results.
 
-Weaknesses and next steps should also be included.
+Both years have not only warm monhs where the number of marriage licenses is high and cold months where it is low, but also in between seasons when the number is increasing or decreasing.
+The analysis could be more nuanced if it had divided the year into 4 instead of 2 by including spring and autumn.
+
+We assumed that obtaining a marriage license comes before conducting the wedding ceremony, but this is not necessarily the case.
+Some couples can choose to get a license without a ceremony, therefore a higher volume in marriage licenses during warm months does not automatically equate to higher demand for wedding ceremonies.
+Further analysis of the number of marriage licenses obtained compared with the number of wedding ceremonies that take place should be conducted to confirm this link.
 

### 2024-01-22 outputs/paper/paper.qmd
changed abstract

@@
 ---
-title: "Getting Hitched: Torontonians Prefer to Get Married During Warm Weather"
+title: "Torontonians Prefer to Get Married in the Warmer Half of the Year"
 author: Diana Liu
@@
 date: 25 January 2024
-abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months.
-By dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March), the number of marriage licenses obtained in Toronto increase significantly during warm months, supporting the hypothesis that Torontonians prefer to get married during warm weather."
+abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months, dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March).
+We found that the number of marriage licenses obtained in 2022 increased by 117% between cold and warm months and 68% in 2023.
+This supports our hypothesis that Torontonians prefer to get married during the warmer half of the year."
 format: pdf
@@
 
-*** Discussion Section
+*insert discussion in intro
 

### 2024-01-24 scripts/00-simulate_data.R
changes to cleaning data

@@ -18,10 +18,10 @@ simulated_marriage_data <-
   tibble(
     Month = 
       format(
-        seq(as.Date("2023/1/1"), by = "month", length.out = 12), format="%B"
+        seq(as.Date("2023/1/1"), by = "month", length.out = 12), format="%Y%B%d"
         ),
     Marriages =
-      round(runif(n = 12, min = 0, max = 1758))
+      round(runif(n = 12, min = 0, max = 2000))
   )
 # simulate deviations from an uniform distribution of the number of marriage
 # licenses obtained in Toronto over 12 months
@@ -30,7 +30,7 @@ simulated_marriage_data
 
 #### Test Simulated Data ####
 simulated_marriage_data$Marriages |> min() >= 0
-simulated_marriage_data$Marriages |> max() <= 1758
+simulated_marriage_data$Marriages |> max() <= 2000
 simulated_marriage_data$Marriages |> class() == 'numeric'
 simulated_marriage_data$Month |> class() == 'character'
 

### 2024-01-24 scripts/02-data_cleaning.R

@@ -3,46 +3,52 @@
 # Author: Diana Liu
 # Date: 16 January 2024
 # Contact: guanzhi.liu@mail.utoronto.ca
-# Pre-Requisits: unedited data is downloaded
+# Pre-Requisites: unedited data is downloaded
 
-#### Workspace setup ####
+#### Work space setup ####
 # install.packages("tidyverse")
 # install.packages("stringr")
 # comment out installations after they are done
 library(tidyverse)
 library(stringr)
+library(dplyr)
 
 #### Clean data ####
 raw_marriages_data <- read_csv("inputs/data/unedited_data.csv")
 
 cleaned_marriages_data <-
   raw_marriages_data |>
-  select(CIVIC_CENTRE, MARRIAGE_LICENSES, TIME_PERIOD) |> # we want to select 
-  #only the relevant columns: civic_centre, marriage_licenses, and time_period
+  select(CIVIC_CENTRE, MARRIAGE_LICENSES, TIME_PERIOD) |>
   filter(CIVIC_CENTRE == "TO")
-# Then we filter on the civic centre so that we are only left with Toronto
+# filtered on the variable civic centre so that I am only left with Toronto
 
-cleaned_marriages_data$TIME_PERIOD <- str_c(cleaned_marriages_data$TIME_PERIOD,
-                                            "-01")
-# We add -01 to the end of the dates so they are formatted correctly as 
-# yyyy-mm-dd
+cleaned_marriages_data$TIME_PERIOD <- as.Date(str_c(cleaned_marriages_data$TIME_PERIOD,
+                                            "-01"))
+# add '-01' to the end of the dates so they are formatted as yyyy-mm-dd so I
+# can filter by dates
 
 cleaned_marriages_data <-
   cleaned_marriages_data |>
   rename(Date = TIME_PERIOD, Marriages = MARRIAGE_LICENSES) |>
-  select(Date, Marriages) |>
+  select(Date, Marriages)
+
+cleaned_marriages_all_years <-
+  cleaned_marriages_data |>
   filter(Date >= as.Date("2022-01-01"))
-# We get rid of the CIVIC_CENTRE column and look at the last two years
-head(cleaned_marriages_data)
+cleaned_marriages_data_all_years$Date <- format(cleaned_marriages_data_all_years$Date, format = "%Y-%B-%d")
+head(cleaned_marriages_data_all_years)
[…]

### 2024-01-24 scripts/02-data_cleaning.R
update dates format

@@ -31,6 +31,7 @@ cleaned_marriages_data <-
   cleaned_marriages_data |>
   rename(Date = TIME_PERIOD, Marriages = MARRIAGE_LICENSES) |>
   select(Date, Marriages)
+head(cleaned_marriages_data)
 
 cleaned_marriages_all_years <-
   cleaned_marriages_data |>
@@ -42,13 +43,15 @@ head(cleaned_marriages_data_all_years)
 cleaned_marriages_data_2022 <-
   cleaned_marriages_data |>
   filter(Date >= as.Date("2022-01-01"), Date <= as.Date("2022-12-31"))
-cleaned_marriages_data_2022$Date <- format(cleaned_marriages_data_2022$Date, format = "%Y-%B-%d")
+cleaned_marriages_data_2022$Date <- format(as.Date(
+  cleaned_marriages_data_2022$Date), format = "%Y-%B-%d")
 head(cleaned_marriages_data_2022)
 
 cleaned_marriages_data_2023 <-
   cleaned_marriages_data |>
   filter(Date >= as.Date("2023-01-01"), Date <= as.Date("2023-12-31"))
-cleaned_marriages_data_2023$Date <- format(cleaned_marriages_data_2023$Date, format = "%Y-%B-%d")
+cleaned_marriages_data_2023$Date <- format(as.Date(
+  cleaned_marriages_data_2023$Date), format = "%Y-%B-%d")
 head(cleaned_marriages_data_2023)
 
 
@@ -56,3 +59,4 @@ head(cleaned_marriages_data_2023)
 write_csv(cleaned_marriages_data, "outputs/data/cleaned_data_all_years.csv")
 write_csv(cleaned_marriages_data_2022, "outputs/data/cleaned_data_2022.csv")
 write_csv(cleaned_marriages_data_2023, "outputs/data/cleaned_data_2023.csv")
+

### 2024-01-24 outputs/paper/paper.qmd
updates

@@
 
+marriage_data$Date <- factor(marriage_data$Date, levels = unique(marriage_data$Date))
+
 marriage_data |>
@@
   geom_text(hjust=0, vjust=0) +
+  scale_x_discrete(breaks=c("2022-January-01","2022-April-01","2022-July-01", "2022-October-01")) +
   theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
@@
   geom_point() +
-  geom_path(color = 'red') +
   theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
+  scale_x_discrete(breaks=c("2022-January-01","2022-June-01","2023-January-01", "2023-June-01")) +
   labs(x = "Month", y = "Marriages", color = "Country")
 ```
-Combining both years, we generate another graph to plot the number of marriage licenses and connect the points with a line so the trend over time is easier to see.
-It is important to note that the line only connect the points and do not represent the rate of change.
-This cyclical nature of more marriage licenses obtained in warm months is evident (@fig-marriages)
+Finally, I plotted both 2022 and 2023 together so the trend over time is easier to see. This cyclical nature of more marriage licenses obtained in warm months is evident (@fig-marriages).
 

### 2024-01-24 scripts/02-data_cleaning.R

@@ -56,7 +56,7 @@ head(cleaned_marriages_data_2023)
 
 
 #### Save data ####
-write_csv(cleaned_marriages_data, "outputs/data/cleaned_data_all_years.csv")
+write_csv(cleaned_marriages_data_all_years, "outputs/data/cleaned_data_all_years.csv")
 write_csv(cleaned_marriages_data_2022, "outputs/data/cleaned_data_2022.csv")
 write_csv(cleaned_marriages_data_2023, "outputs/data/cleaned_data_2023.csv")
 

### 2024-01-24 scripts/00-simulate_data.R
updated comments

@@ -7,7 +7,7 @@
 
 #### Workspace setup ####
 # install.packages("tidyverse")
-# We can comment out the installation after tidyverse has been installed
+# comment out the installation after tidyverse has been installed
 library(tidyverse)
 
 
@@ -32,5 +32,4 @@ simulated_marriage_data
 simulated_marriage_data$Marriages |> min() >= 0
 simulated_marriage_data$Marriages |> max() <= 2000
 simulated_marriage_data$Marriages |> class() == 'numeric'
-simulated_marriage_data$Month |> class() == 'character'
 

### 2024-01-24 scripts/01-download_data.R

@@ -21,14 +21,11 @@ toronto_marriages <-
   # Developers" tab of the relevant page from Open Data Toronto
   # https://open.toronto.ca/dataset/marriage-licence-statistics/
   list_package_resources("e28bc818-43d5-43f7-b5d9-bdfb4eda5feb") |>
-  # we are only interested in the .csv data file
 filter(name == "Marriage Licence Statistics Data.csv") |>
-  # Having reduced the dataset to one row we can get the resource
   get_resource()
 
 
 #### Save data ####
-# After downloading the data, we can save it under a descriptive name
 write_csv(
   x = toronto_marriages,
   file = "inputs/data/unedited_data.csv"

### 2024-01-24 scripts/03-test_data.R

@@ -8,14 +8,13 @@
 
 #### Workspace setup ####
 # install.packages("tidyverse")
-# We can comment out the installation after tidyverse has been installed
+# comment out the installation after tidyverse has been installed
 library(tidyverse)
 
 #### Test data ####
 marriage_data <- read_csv("outputs/data/cleaned_data.csv")
 
-marriage_data$Marriages |> min() >= 563
-marriage_data$Marriages |> max() <= 1649
+marriage_data$Marriages |> min() >= 0
+marriage_data$Marriages |> max() <= 2000
 marriage_data$Marriages |> class() == 'numeric'
-marriage_data$Month |> class() == 'character'
 

### 2024-01-24 outputs/paper/paper.qmd
updated comments
updates writing

@@
 date: 25 January 2024
-abstract: "We examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months, dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March).
-We found that the number of marriage licenses obtained in 2022 increased by 117% between cold and warm months and 68% in 2023.
-This supports our hypothesis that Torontonians prefer to get married during the warmer half of the year."
+abstract: "I examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months, dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March).
+I found that the number of marriage licenses obtained in 2022 increased by 117% between cold and warm months and 68% in 2023.
+This supports the hypothesis that Torontonians prefer to get married during the warmer half of the year."
 format: pdf
@@
 # Introduction
-According to @citebusinessinsider, summer is the hottest time to get married due to more dress options, the opportunity to have an outdoor wedding, and relatively easier travel among other reasons, but is this actually true in Toronto?
-Toronto is a city known for cold weather in the winter with snow from October to March (@citeurbanclimate).
-This means that we expect the amount of marriage licenses obtained in Toronto should increase during the warm months of April through September and decrease during the cold months of October through March.
+According to @citebusinessinsider, summer is the hottest time to get married in the United States, but I want to know if this is true in Toronto as well.
+Toronto is a city known for cold weather in the winter with snow from October to March (@citeurbanclimate), so it makes sense for Torontonians to prefer the warmer months of April to September.
+This means that we expect the amount of marriage licenses obtained in Toronto should be higher during the warm months of April through September than the cold months of October through March.
 By knowing whether or not more marriages occur during the summer months, prospective couples in Toronto can plan ahead and avoid peak seasons for applying for a marriage license and any delays that result.
 
-In the Data section, we download marriage license data from opendatatoronto(@citeopendata), a database maintained by the City of Toronto.
-This dataset features the number of marriage licenses issued in Toronto by month, beginning January 1 2011.
-We will be looking at data from 2023 and 2022, as well as any changes in the number of marriage licenses between the two years.
+In the Data section, I download marriage license data from opendatatoronto(@citeopendata), a database maintained by the City of Toronto.
+This data set features the number of marriage licenses issued in Toronto by month, beginning January 1 2011.
+I will only be looking at data from 2023 and 2022, this is because some data is missing in 2021, and covid-19 lock downs means that 2020 data is inaccurate.
 
-We formulate our hypothesis to be that there are more marriage licenses obtained in warm months of April to September than cold months of October to March because Torontonians prefer to get married during the warmer half of the year.
-We analyzed the data in the Results section by plotting the number of licenses against the month in which they were obtained so we can see the change in the number of marriage licenses from month to month.
-Since there are only 12 data points in each graph, we are also able to label each observation with the exact number of marriage licenses issued.
-Then we calculated the total amount and the average amount of marriage licenses in the warm months and cold months of each year, and the percent change between them.
-Our results show that our hypothesis is correct with the number of marriage licenses steadily increasing from February to May, peaking around July, then decreasing between September and November before hitting its lowest in January.
-This cyclic nature can be observed for both 2022 and 2023.
+I formulated my hypothesis to be that there are more marriage licenses obtained in warm months of April to September than cold months of October to March because Torontonians prefer to get married during the warmer half of the year.
+I analyzed the data in the Results section by plotting the number of licenses against the month in which they were obtained so we can see the change in the number of marriage licenses from month to month.
+Since there are only 12 data points in each graph, I labeled each observation with the exact number of marriage licenses issued.
+Then I calculated the total amount and the average amount of marriage licenses in the warm months and cold months of each year, and the percent change between them.
+My results show that the hypothesis is correct with the number of marriage licenses steadily increasing from February to May, peaking around July, then decreasing between September and November before hitting its lowest in January.
 
-*insert discussion in intro
+The cyclical appearance of the number of marriage licenses in both 2023 and 2023...
 
@@
 ## Weaknesses and Next Steps
-A weakness in our analysis is the small quantity of data that was used to come to our conclusion.
+A weakness in my analysis is the small quantity of data that was used to come to our conclusion.
 While the pattern of increased marriage licenses was present in both 2022 and 2023, this might not have been the case in prior years.

### 2024-01-25 outputs/paper/paper.qmd
update on writing

@@
 date: 25 January 2024
-abstract: "I examine marriage licenses obtained in the city of Toronto in the year 2022 and 2023 by months, dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March).
+abstract: "In this paper I examine marriage licenses obtained in the city of Toronto over time in 2022 and 2023 by months, dividing the year into warm months (April, May, June, July, August, September) and cold months (October, November, December, January, Febuary, March).
 I found that the number of marriage licenses obtained in 2022 increased by 117% between cold and warm months and 68% in 2023.
-This supports the hypothesis that Torontonians prefer to get married during the warmer half of the year."
+This suggests that Torontonians prefer to get married during the warmer half of the year.
+Couples planning their wedding should take into account the higher demand for marriages in the warmer months to plan accordingly."
 format: pdf
@@
 bibliography: references.bib
+toc: true
 ---
@@
 According to @citebusinessinsider, summer is the hottest time to get married in the United States, but I want to know if this is true in Toronto as well.
-Toronto is a city known for cold weather in the winter with snow from October to March (@citeurbanclimate), so it makes sense for Torontonians to prefer the warmer months of April to September.
+Toronto is a city known for cold weather in the winter with snow from October to March (@citeurbanclimate), so it makes sense for Torontonians to prefer the warmer months of April to September for getting married.
 This means that we expect the amount of marriage licenses obtained in Toronto should be higher during the warm months of April through September than the cold months of October through March.
 By knowing whether or not more marriages occur during the summer months, prospective couples in Toronto can plan ahead and avoid peak seasons for applying for a marriage license and any delays that result.
+To examine the trend in marriage licenses issued over time, the paper is organized into the following sections: Data, Results, Discussion, and Conclusion.
 
-In the Data section, I download marriage license data from opendatatoronto(@citeopendata), a database maintained by the City of Toronto.
+In the Data section, I download marriage license data from opendatatoronto (@citeopendata), a database maintained by the City of Toronto.
 This data set features the number of marriage licenses issued in Toronto by month, beginning January 1 2011.
@@
 
-I formulated my hypothesis to be that there are more marriage licenses obtained in warm months of April to September than cold months of October to March because Torontonians prefer to get married during the warmer half of the year.
-I analyzed the data in the Results section by plotting the number of licenses against the month in which they were obtained so we can see the change in the number of marriage licenses from month to month.
+To examine if there are more marriage licenses obtained in warm months of April to September than cold months of October to March, I analyzed the data in the Results section by plotting the number of licenses against the month in which they were obtained so the change in the number of marriage licenses from month to month can be seen.
 Since there are only 12 data points in each graph, I labeled each observation with the exact number of marriage licenses issued.
-Then I calculated the total amount and the average amount of marriage licenses in the warm months and cold months of each year, and the percent change between them.
+Then I calculated the total amount and the average amount of marriage licenses in the warm months and cold months of each year, and the percent change between cold and warm months.
 My results show that the hypothesis is correct with the number of marriage licenses steadily increasing from February to May, peaking around July, then decreasing between September and November before hitting its lowest in January.
 
-The cyclical appearance of the number of marriage licenses in both 2023 and 2023...
+The cyclical appearance of the number of marriage licenses occurs in both 2022 and 2023 (@fig-marriages).
+Usually marriage licenses are obtained before a wedding ceremony, so the number of weddings is likely to follow a similar trend.
+This can explain why more people decide to apply for marriage licenses in the warm months, as it is likely due to wanting a summer wedding with better weather, more outfit options, and the option for outdoor weddings.
 
 # Data {#sec-data}
-Our data is Marriage Licence Statistics from Open Data Toronto (@citeopendata) which contains data sets maintained by the City of Toronto.
-The Marriage Licence Statistics dataset consists of monthly number of marriage licenses obtained from 2011 to 2023 in the Greater Toronto Area, it was last updated 2024-01-14.
-No similar data sets could have been used because this dataset is the only one of marriage licences.
-Looking at (@fig-raw_toronto_marriages), the Marriage Licence Statistics dataset contains only four variables: x_id, civic centres, marriage licenses, and date, but only civic centres, marriage licenses, and date were used in our analysis.
-The data was cleaned and analysed using the statistical software R (@citeR) with the assistance of tidyverse (@citetidy), dyplr (@citedyplr), ggplot2 (@citeggplot2), tinytex (@citetiny), gt (@citegt), and stringr (@stringr).
+The data is Marriage Licence Statistics from Open Data Toronto (@citeopendata) which contains data sets maintained by the City of Toronto.
+The Marriage Licence Statistics data set consists of monthly number of marriage licenses obtained from 2011 to 2023 in the Greater Toronto Area, it was last updated 2024-01-14.
+No similar data sets could have been used because this data set is the only one of marriage licences.
+Looking at (@fig-raw_toronto_marriages), the Marriage Licence Statistics data set contains only four variables: x_id, civic centres, marriage licenses, and date, but only civic centres, marriage licenses, and date were used in the analysis.
+The data was cleaned and analysed using the statistical software R (@citeR) with the assistance of tidyverse (@citetidy), dyplr (@citedyplr), ggplot2 (@citeggplot2), tinytex (@citetiny), gt (@citegt), and stringr (@citestringr).
 
-We selected the past two years due to some 2021 data being missing and the fact that Covid-19 in 2020 caused a significant decrease in the number of marriage licenses that were obtained all year compared to other years (@citesage).
+I selected only 2022 and 2023 due to some 2021 data being missing and the fact that Covid-19 in 2020 caused a significant decrease in the number of marriage licenses that were obtained all year compared to other years (@citesage).
 
@@
 During the data cleaning process, we filter out ET, NY, and SC so we can focus on Toronto.
-After filtering, we will not need the variable anymore (@fig-cleaned_toronto_marriages).
+After filtering, the variable is no longer needed (@fig-cleaned_toronto_marriages_2022).
 
@@
   There are 12 observations per year for each month (@fig-cleaned_toronto_marriages_2022).
-This makes 24 observations for 2022-23 between 472 and 1758, with an average of 1043.3 marriage licenses obtained.
+This makes 24 observations for 2022 to 2023 with a min of 472 and max of 1758, with an average of 1043.3 marriage licenses obtained each month.
 
@@
 TIME_PERIOD is the month in which the marriage licenses were obtained in a yyyy-mm date format.
-When we clean the data, we must add a -dd to the end of each date value in order for the dates to be in an unambiguous format.
-Then the date is filtered by year to separate 2022 and 2023 from the rest of the dataset.
+When I clean the data, I added a '-01' to the end of each date value in order for the dates to be in an unambiguous format.
+Then the date is filtered by year to separate 2022 and 2023 from the rest of the data set and reformatted to be in a 'yyyy-month-dd' format so it is easier to distinguish the month from the day.
 
@@
 ```
-After the data we need has been cleaned, it is saved into 3 .csv files, one for 2022 and another for 2023, both of which have 12 observations one for each month.
-The third .csv file conains both years and has 24 observations.
+After the data I need has been cleaned, it is saved into 3 .csv files, one for 2022, another for 2023, and the third contains both years.
 The only columns that remain in any file are Date and Marriages (@fig-cleaned_toronto_marriages_2022).
@@
 # Results
-In order to determine if there is a difference in the amount of marriage licenses issued in Toronto between warm months (April to September) compared to cold months (October to March), we plot the number of marriage licenses for each month separately for 2022, 2023 and both years together.
+In order to determine if there is a difference in the amount of marriage licenses issued in Toronto between warm months (April to September) compared to cold months (October to March), I plotted the number of marriage licenses for each month separately for 2022, 2023 and both years together.
 
-## 2022 Marriage Licenses
-(@fig-2022_marriages)
+## 2022
 ```{r}
 #| label: fig-2022_marriages
-#| fig-cap: Number of marriage licenses issued in Toronto in 2022
+#| fig-cap: Trend in marriage licenses issued over time in 2022
 #| echo: false
@@
   geom_text(hjust=0, vjust=0) +
-  scale_x_discrete(breaks=c("2022-January-01","2022-April-01","2022-July-01", "2022-October-01")) +
-  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
-  labs(x = "Month", y = "Marriages", color = "Country")
+  scale_x_discrete(breaks=c("2022-April-01", "2022-September-01")) +
+  theme(axis.text.x = element_text(angle = 0, vjust = 0.5), plot.title = element_text(size=12)) +
+  labs(x = "Month", y = "Marriages", color = "Country", title = "Marriage Licenses Issued in Toronto in 2022")
 ```
@@
 
-We used ggplot to plot each marriage license observation for each month, then we connected the points so the trend over time is easier to observe.
-Looking at @fig-2022_marriages, we can see that January has the lowest amount marriage licenses being issued of 472.
+I used ggplot to plot each marriage license observation for each month so the trend in the number of marriage licenses over time in 2022 can be observed (@fig-2022_marriages).
+January has the lowest amount marriage licenses being issued of 472.
 A slight increase of 62 licenses occurs in February, followed by an increase in in March of 684, more than doubling the amount in February.
@@
 #| label: fig-2023_marriages
-#| fig-cap: Number of marriage licenses issued in Toronto in 2023
+#| fig-cap: Trend in marriage licenses issued over time in 2023
 #| echo: false
@@
   geom_text(hjust=0, vjust=0) +
-  scale_x_discrete(breaks=c("2022-January-01","2022-April-01","2022-July-01", "2022-October-01")) +
-  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
-  labs(x = "Month", y = "Marriages", color = "Country")
+  scale_x_discrete(breaks=c("2023-April-01", "2023-September-01")) +
+  theme(axis.text.x = element_text(angle = 0, vjust = 0.5), plot.title = element_text(size=12)) +
+  labs(x = "Month", y = "Marriages", color = "Country", title = "Marriage Licenses Issued in Toronto in 2023")
 ```
@@
 The decrease like 2022, starts in September and continues until November.
-
 In 2023 there is a $(7026-4146)/4146\approx68\%$ increase between warm and cold months.
@@
 $$
-The results indicate that our hypothesis is correct. There are more marriage licenses issued in warm months (April to September) than cold months (October to March).
+The results indicate that the hypothesis is correct. There are more marriage licenses issued in warm months (April to September) than cold months (October to March).
 
@@
 #| label: fig-marriages
-#| fig-cap: Number of marriage licenses issued in Toronto in 2022 and 2023
+#| fig-cap: Trend in marriage licenses issued over time from 2022 to 2023
 #| echo: false
@@
   geom_point() +
-  theme(axis.text.x = element_text(angle = 0, vjust = 0.5)) +
-  scale_x_discrete(breaks=c("2022-January-01","2022-June-01","2023-January-01", "2023-June-01")) +
-  labs(x = "Month", y = "Marriages", color = "Country")
+  theme(axis.text.x = element_text(angle = 0, vjust = 0.5), plot.title = element_text(size=12)) +
+  scale_x_discrete(breaks=c("2022-April-01","2022-September-01","2023-April-01", "2023-September-01")) +
+  labs(x = "Month", y = "Marriages", color = "Country", title = "Marriage Licenses Issued in Toronto in 2022 and 2023")
 ```
@@
 ## Findings
-In both 2022 and 2023, there was more marriage licenses issued in warm months than cold ones, 117% more in 2022 and 68% more in 2023.
+In both 2022 and 2023, there was more marriage licenses issued in warm months than cold ones, 117% more in 2022 and 68% more in 2023 (@fig-2022_marriages)(@fig-2023_marriages).
 This confirms our hypothesis of more marriages taking place from April to September.
-
 Compared with the 2022 data, the total number of marriage licenses in 2023 only changed by $(12334-12706)/12706 = −0.0292\approx-2.92\%$.
@@
 Since applying for a marriage license comes before the actual wedding ceremony, we can infer that more licenses equate to more weddings.
-This means that there is more demand for venues, photographers, and catering for weddings from April to September making these services harder to book and potentially more expensive.
+Then the appeal of summer weddings can be used to explain the increase in marriage licenses.
+Weddings in warmer months allows for more dress options, better weather, and outdoor weddings.
+July and August are also some of the most popular times for vacation which make it easier to book travel arrangements for guests and also opens up possibilities of destination weddings
 
+The popularity of weddings in warmer months of the year, especially June, July, and August means that there is more demand for venues, photographers, and catering for weddings from April to September making these services harder to book and potentially more expensive.
 Prospective couples should consider the trend of higher volume marriage license applications in the warm months when applying for their marriage license because although many Torontonians prefer getting married in the warm month, the higher volume of marriage license application could cause delays.
-The higher demand for wedding ceremonies should also be a part of budgeting for their weddings.
+The higher demand for wedding ceremonies should also be a part of budgeting for their weddings as increased demand usually correlates with increased prices.
 
 ## Weaknesses and Next Steps
-A weakness in my analysis is the small quantity of data that was used to come to our conclusion.
+A weakness in my analysis is the small quantity of data that was used to come to my conclusion.
 While the pattern of increased marriage licenses was present in both 2022 and 2023, this might not have been the case in prior years.
-Performing the same analysis on years 2011 to 2021 will confirm our results.
+Performing the same analysis on years 2011 to 2021 will confirm the results.
 
@@
 
-We assumed that obtaining a marriage license comes before conducting the wedding ceremony, but this is not necessarily the case.
-Some couples can choose to get a license without a ceremony, therefore a higher volume in marriage licenses during warm months does not automatically equate to higher demand for wedding ceremonies.
+This paper assumed that obtaining a marriage license comes before conducting the wedding ceremony, but this is not necessarily the case.
+Some couples can choose to get a license without a ceremony, therefore a higher volume in marriage licenses during warm months does not automatically equate to more wedding ceremonies.
 Further analysis of the number of marriage licenses obtained compared with the number of wedding ceremonies that take place should be conducted to confirm this link.
+Moreover, marriage license data does not take into consideration common law marriages nor wedding ceremonies that occurs without a license.
+
+# Conclusion
+This paper investigated whether or not Torontonians prefer to get married during the warm months of the year, April to September.
+My results show that warmer months tend to have a higher number of marriage licenses issued, with June, July, and August being the most popular months.
+The amount of marriage licenses issued each month tends to increase from January to June and decrease from August to December.
+This is likely caused by the preference of most couples to conduct the wedding ceremony in warmer weather which allows for more options in terms of venue and clothing and better weather.
+Couples considering getting married in Toronto should weigh the high demand for marriage licenses and wedding ceremonies which can result in higher prices, delays, and bookings far in advance with the advantages of having a summer wedding.
 

### 2024-01-25 outputs/paper/paper.qmd
updates

@@
 
-raw_marriage_data <- read_csv("/cloud/project/inputs/data/unedited_data.csv")
+raw_marriage_data <- read_csv("/inputs/data/unedited_data.csv")
 gt(head(raw_marriage_data))
@@
 
-cleaned_marriage_data_2022 <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
+cleaned_marriage_data_2022 <- read_csv("/outputs/data/cleaned_data_2022.csv")
 gt(head(cleaned_marriage_data_2022))
@@
 #| warning: false
-marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
+marriage_data <- read_csv("/outputs/data/cleaned_data_2022.csv")
 
@@
 #| include: false
-marriage_data_2022 <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
+marriage_data_2022 <- read_csv("/outputs/data/cleaned_data_2022.csv")
 summary(marriage_data_2022$Marriages)
@@
 #| warning: false
-marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data_2023.csv")
+marriage_data <- read_csv("/outputs/data/cleaned_data_2023.csv")
 
@@
 #| include: false
-marriage_data_2023 <- read_csv("/cloud/project/outputs/data/cleaned_data_2023.csv")
+marriage_data_2023 <- read_csv("/outputs/data/cleaned_data_2023.csv")
 summary(marriage_data_2023$Marriages)
@@
 #| warning: false
-marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data_all_years.csv")
+marriage_data <- read_csv("/outputs/data/cleaned_data_all_years.csv")
 
